Carbonate chemistry at Ny-Ålesund

### 2021-04-02 awipev-CO2.Rmd
removed use of cowplot

p <- cowplot::plot_grid(p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m, ncol = 1)
pngfile <- "figures/air-sea_CO2_flux.png"
ggsave(
  pngfile, 
  p, 
  device = agg_png, 
  width = 6.6, height = 10, units = "cm", res = 300,
  scaling = 0.4
)
rm(p_f_air_sea)
knitr::include_graphics(pngfile)
```

>>>>

p <- p_f_air_sea / p_f_air_sea_d / p_f_air_sea_m
ggsave(filename = "figures/air-sea_CO2_flux.png", plot = p, width = 20, units = "cm")
#p <- cowplot::plot_grid(p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m, ncol = 1)
#pngfile <- "figures/air-sea_CO2_flux.png"
# ggsave(
#   pngfile, 
#   p, 
#   device = agg_png, 
#   width = 6.6, height = 10, units = "cm", res = 300,
#   scaling = 0.4
# )
knitr::include_graphics("figures/air-sea_CO2_flux.png")
#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
```
